Interactive effects of drought and habitat fragmentation on vital rates of an understory tropical plant

### 2021-02-19 analysis/paper/paper.Rmd
edits.  I hope sentence wrap "sticks" this time.

```{r}
cap <- "Smooth effect of lagged SPEI on survival. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Contour lines correspond to a change of 0.002. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale."

@@

```{r}
cap <- "Smooth effect of lagged SPEI on plant growth. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Contour lines correspond to a change of 0.1. "
```

<!--# this is the raw fitted values of the tensor product smooth. That is, I have not shifted this by adding the model intercepts like I did in the last figure.  Not sure if the effect size should actually be interpreted as a additive change in size, but I think so maybe?  If that's true, then the predicted effect of SPEI on size in year t+1 is extremely small compared to the effect of size in year t. -->

@@

```{r}
cap <- "Smooth effect of lagged SPEI on flowering probability. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Contour lines correspond to a change of 0.001. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale."
```

>>>>

```{r}
cap <- "Smooth effect of lagged SPEI on survival in a) continuous forest and b) 1-ha fragments. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale. Contour lines correspond to a change of 0.002. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October)."

@@

```{r}
cap <- "Smooth effect of lagged SPEI on plant growth for a) continuous forest and b) 1-ha fragments. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function. Contour lines correspond to a change of 0.05. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October)."
```

@@

```{r}
cap <- "Smooth effect of lagged SPEI on flowering probability. Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale. Contour lines correspond to a change of 0.001. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October)."
```
